### 2020-10-19 tex/initial-presentation.tex
Complete initial presentation.

  \begin{frame}{Low-Code Architecture}
    \begin{itemize}
      \item pre-built application components
      \item graphical user interface for creating application logic as well as
    \end{itemize}
  \end{frame}

  \begin{frame}{Model-Driven Architecture}
    \begin{itemize}
      \item
    \end{itemize}
  \end{frame}

  \begin{frame}{Criticisms}
    \begin{itemize}
      \item Unsuitable for implementing scalable and mission-critical applications.
      \item Do these approaches actually make development easier and cheaper?
      \item Increase in unsupported applications built by shadow IT.
    \end{itemize}
  \end{frame}

  \begin{frame}{Planned Project Procedure}
    \begin{itemize}
      \item evaluate Low-Code tools
      \item evaluate Model-Driven tools
      \item pick two to three of each
      \item compare the two sets with each other
      \item check if a tool fulfils
    \end{itemize}
  \end{frame}
\end{document}

>>>>

  \begin{frame}{Low-Code Architecture}
    \begin{itemize}
      \item provides pre-built application components
      \item graphical user interface for creating both the
            application logic as well as the user interface
      \item typically aimed at end-users rather than developers
    \end{itemize}
  \end{frame}

  \begin{frame}{Model-Driven Architecture}
    \begin{itemize}
      \item provides a set of guidelines for the structuring of specifications
      \item code (fully or partially) generated from models, e.g. from UML diagrams
      \item aimed at developers to speed up development
    \end{itemize}
  \end{frame}

  \begin{frame}{Criticisms}
    \begin{itemize}
      \item Low-Code Architecture
        \begin{itemize}
          \item Unsuitable for implementing scalable and mission-critical applications.
          \item Increase in unsupported applications built by shadow IT,
                i.e. applications which are not controlled by a company's IT department.
        \end{itemize}
      \item Model-Driven Architecture
        \begin{itemize}
          \item UML diagrams lack details included in the code itself.
          \item “the Code is the design” - Should models be derived from code instead of code from models?
        \end{itemize}
      \item Do these approaches actually make development easier and cheaper?
    \end{itemize}
  \end{frame}

  \begin{frame}{Planned Project Procedure}
    \begin{itemize}
      \item Evaluate a set of Low-Code tools.
      \item Evaluate a set of Model-Driven tools.
      \item For each tool, determine what it can and can't do.
      \item Compare the two sets with each other and draw some conclusions.
    \end{itemize}
  \end{frame}
\end{document}
